Complex Analysis of Askaryan Radiation: UHE-$\nu$ Identification and Reconstruction using the Hilbert Envelope of Observed Signals

### 2025-10-12 template.tex
last commit

\title{Complex Analysis of Askaryan Radiation: UHE-$\nu$ Identification and Reconstruction via the Hilbert Envelope of Observed Signals}

@@

Cosmic neutrinos with energies up to 100 PeV have been detected by the IceCube and KM3NeT collaborations \cite{10.1126/science.1242856,aartsen2013first-bff,collaboration2016observation-03b,collaboration2018neutrino-2a0,collaboration2021detection-6fa,collaboration2022evidence-a08,collaboration2023observation-08b,collaboration2025observation-22f}. Previous analyses indicate that the discovery of UHE-$\nu$ flux above 5 PeV requires large Askaryan-class detectors \cite{10.1103/physrevd.98.062003}.  UHE-$\nu$ could reveal the source of ultra-high energy cosmic rays (see sections 3.1-3.3 of \cite{10.48550/arxiv.2008.04323}).  Further, studying electroweak interactions at these energies is impossible on Earth, and Askaryan-class neutrino detectors provide new data (see section 3.4 of \cite{10.48550/arxiv.2008.04323}).

@@

Askaryan-class detectors actually observe voltage traces that represent the RF detection channel response, convolved with $\vec{E}$-fields that have propagated through kilometers of polar ice.  NuRadioMC accounts for these effects by incorporating measurements from years of lab and field work \cite{10.1016/j.astropartphys.2014.09.002,10.3189/2015jog14j214,10.3189/2015jog15j057,saltzberg,10.1103/PhysRevD.74.043002,ask_ice,10.1140/epjc/s10052-020-7612-8,Barwick:2018497,ALLISON201963,10.1088/1748-0221/15/09/p09039,deaconu2018measurements-182,welling2024brief-b47}.  In this work, we present the first fully analytic Askaryan model in the time-domain that matches the observed voltage traces.  In practice, it is common to compute the Hilbert envelope of voltage traces from RF channels before cross-correlating them.  This is done to remove oscillations introduced by the RF antennas in the channels, which can confuse cross-channel timing and reconstruction.  Our calculations include both the voltage trace, and the Hilbert envelope of the trace.  The work is organized as follows.  Units, definitions, and notational conventions are given in Sec. \ref{sec:unit}.  The calculations of the observed voltage trace and Hilbert envelope of the trace are given in Sec. \ref{sec:onc}.  These results are compared to NuRadioMC output in Sec. \ref{sec:sim}.  In Sec. \ref{sec:conc}, the key findings are summarized.

@@

The analysis is based on two analytic functions: the Askaryan signal, $s(t)$, and the RF channel response, $r(t)$.  The RF detection channel is a linear, time-invariant DSP system.  Thus, the observed voltage trace in an Askaryan-class detector is the convolution of $r(t)$ and $s(t)$, $r(t) * s(t)$.  Let $\hat{s}(t)$ represent the Hilbert transform of $s(t)$, and let $j=\sqrt{-1}$.  The \textit{analytic signal} and \textit{signal envelope} are defined by

@@

The $n_{\rm max}$ parameter is the maximum number of excess negative cascade charges, and the overall RF amplitude, $E_{\rm 0}$, is propotional to $n_{\rm max} a$ \cite{10.1103/physrevd.65.016003}.  JCH+AC and HH2022 demonstrated that the cutoff frequency $\omega_{\rm 0}$ is related to the ICD and the cascade form factor \cite{10.1016/j.astropartphys.2017.03.008,PhysRevD.105.123019}.  Monte Carlo simulations have shown that the lateral dependence of the ICD is exponentially distributed \cite{zhs,10.1016/j.astropartphys.2017.03.008}.  JCH+AC derived the form factor by modeling the lateral component of the ICD as an exponential distribution.  Finally, the authors of HH2022 have shown that the parameter $p$ is related to $\sigma_t$, the pulse width of $s(t)$ \cite{PhysRevD.105.123019}:

@@

The parameters in Eq. \ref{eq:s_full} that do not depend on time can be folded into a single constant, $E_0$, leaving only the time-dependence.  From now on, let $t$ refer to $t_{\rm r}$, without the subscript.  The signal model $s(t)$ is
\begin{equation}
s(t) = -E_0 t e^{-\frac{1}{2}\left(t/\sigma_t\right)^2} \label{eq:s}
\end{equation}
This is the \textit{off-cone} equation from \cite{PhysRevD.105.123019}.  The parameter $\sigma_{\rm t}$ is the pulse width, and it depends two quantities: $a$ and $\Delta\theta$ (Eq. \ref{eq:uncert}).  The parameter $E_0$ is the amplitude normalization, and the dependencies on other parameters can be determined from Eq. \ref{eq:s_full} and Tab. \ref{tab:param}.  To achieve the goal of $\mathcal{E}_{\rm r * s}(t)$, the Hilbert transform and analytic signal of $s(t)$ are required.  The Hilbert transform $\widehat{s}(t)$ is equivalent to the convolution of $s(t)$ and the tempered distribution $h(t) = 1/(\pi t)$.  The implication in the Fourier domain is that the negative frequencies in the spectrum of $\hat{s}(t)$ vanish, while the positive ones are doubled.  Let the $\sgn(f)$ be $-1$ if $f<0$, $0$ if $f=0$, and $1$ if $f>1$, and let $S(f)$ be the Fourier transform of $s(t)$.  The Fourier transform of the analytic signal $s_a(t)$ is
\begin{equation}
\mathcal{F}\lbrace s_{\rm a}(t) \rbrace_{f} = S_{\rm a}(f) = S(f)(1+\sgn{f}) \label{eq:sa_1}
\end{equation}
Thus, if $f<0$, $S_a(f) = 0$, and $S_a(f) = 2S(f)$ if $f\geq 0$.  Taking the inverse Fourier transform of Eq. \ref{eq:sa_1}, the analytic signal may be written in terms of $S(f)$:
\begin{equation}
s_{\rm a}(t) = 2\int_{0}^{\infty} S(f) e^{2\pi j f t} df \label{eq:sa_2}
\end{equation}
 The Fourier transform of Eq. \ref{eq:s} is
\begin{equation}
S(f) = E_0 \sigma_t^3 (2\pi)^{3/2} j f e^{-2\pi^2 f^2 \sigma_t^2}
\end{equation}
Using the gaussian spectral width $\sigma_{\rm f}$ from \cite{10.1016/j.astropartphys.2017.03.008}, and the guassian width of $s(t)$ from \cite{PhysRevD.105.123019}, it was shown in \cite{PhysRevD.105.123019} that the uncertainty principle holds for off-cone signals:
\begin{equation}
\sigma_t \sigma_f \geq \frac{1}{2\pi}
\end{equation}
The equality is reached in the limit the far-field parameter limits to zero: $\eta \to 0$.  This makes the signal spectrum
\begin{equation}
S(f) = E_0 \sigma_t^3 (2\pi)^{3/2} j f e^{-\frac{1}{2}\left(f/\sigma_f\right)^2} \label{eq:spec}
\end{equation}
Inserting $S(f)$ into Eq. \ref{eq:sa_2}, $s_{\rm a}(t)$ is
\begin{equation}
s_{\rm a}(t) = \frac{E_0 \sigma_t^3 (2\pi)^{3/2}}{\pi} \frac{d}{dt}\int_0^{\infty} e^{-\frac{1}{2}\left(f/\sigma_f\right)^2} e^{2\pi j f t} df \label{eq:sa_3}
\end{equation}
 Let $k^2/4 = \frac{1}{2}\left(f/\sigma_f\right)^2$, and $x = t/(\sqrt{2}\sigma_t)$.  Equation \ref{eq:sa_3} can be broken into real and imaginary parts:
\begin{align}
s_{\rm a}(t) &= \frac{E_0 \sigma_{\rm t}}{\sqrt{2\pi}}\frac{dI}{dx} \\
\Re\lbrace I \rbrace &= \int_0^{\infty} e^{-k^2/4}\cos(kx) dk \\
\Im\lbrace I \rbrace &= \int_0^{\infty} e^{-k^2/4}\sin(kx) dk
\end{align}
The real part of $I$ is even, so it can be extended to $(-\infty,\infty)$ if it is multiplied by $1/2$.  The result is
\begin{equation}
\Re\lbrace I \rbrace = \sqrt{\pi} e^{-x^2}
\end{equation}
The imaginary part of $I$ is proportional to the \textit{Dawson function, $D(x)$} \cite{NIST:DLMF}:
\begin{equation}
\Im\lbrace I\rbrace = 2 D(x)
\end{equation}
 The overall analytic signal, $s_a(t)$, is
\begin{equation}
s_a(t) = -E_0 \left(t e^{-\frac{1}{2}\left(t/\sigma_t\right)^2} - \frac{2 j\sigma_t}{\sqrt{2\pi}} \frac{dD(x)}{dx}\right) \label{eq:sa_4}
\end{equation}
The envelope of the signal, $\mathcal{E}_s(t)$, is the magnitude of Eq. \ref{eq:sa_4}.  Though $D(x)$ is not evaluated analytically, a high-precision algorithm for computing $D(x)$ was given in \cite{10.1063/1.4822832}.  As expected, $|s_a(0)| \neq 0$, since $dD(x)/dx = 1 - 2x D(x)$.

@@

To reduce uncertainties, the Hilbert envelope of observed data is used in cross-correlations instead of the original signals.  Thus, an analytic prediction for the Hilbert envelope of the observed data would an effective signal template.  An assumption must be made, however, for the RF channel response, $r(t)$.  The RLC impulse response was first used by RICE at the South Pole at a model for RF dipole channels \cite{10.1103/PhysRevD.85.062004}.  The RLC damped oscillator is a suitable circuit model for the RF dipole channels for two reasons.  First, dipoles respond within a bandwidth centered around a resonance frequency, just as RLC circuits do.  Second, RF dipole  channels are used in RICE, RNO-G, and the proposed IceCube Gen2 because these channels must fit inside cylindrical ice boreholes \cite{10.1088/1748-0221/16/03/p03025,10.48550/arxiv.2008.04323}.  Thus, the model chosen for $r(t)$ is the damped oscillation of an RLC circuit.

@@

NuRadioMC was used to generate UHE-$\nu$ interactions in a cylindrical ice volume (see Tab. \ref{tab:1}).  The 100 PeV interactions included charged and neutral electroweak currents, and the LPM effect.  The Askaryan model used in NuRadioMC was AHRZ2020 \cite{PhysRevD.101.083005}.  AHRZ2020 is a \textit{semi-analytic} parameterization of the Askaryan effect, in which a vector potential $\vec{A}(\vec{r},t)$ is convolved with the profile of the net charge in the UHE-$\nu$ cascade.  AHRZ2020 accounts for sub-cascades and the LPM effect, and it has been validated against MC simulations \cite{zhs,10.1103/physrevd.84.103003}.  The Askaryan model used in NuRadioMC for this analysis was \textit{not} HH2022, so correlations between MC output and Eqs. \ref{eq:final}-\ref{eq:final2} is solely on physical grounds.

@@

\begin{equation}
\ln\Lambda = \left( \frac{c\sigma_t}{c_{\rm em/had} \Delta\theta_{\rm rms}\sin\theta_{\rm C}} \right)^2 \label{eq:lnLambda}
\end{equation}

Using Eqs. 10 and 12 from HH2022 (\cite{PhysRevD.105.123019}), $c_{\rm em}$ and $c_{\rm had}$ were found to be 0.80 and 0.93 meters, respectively (FWHM, $R=0.5$).  Using Eq. \ref{eq:lnLambda}, the $\sigma_t$ results from the optimized envelope fits to UHE-$\nu$ signals may be used to deduce the logarithm of the UHE-$\nu$ cascade, $\log_{10} E_{\rm C}$.  First, converting to the base-10 logarithm introduces a factor of $\ln(10)$ in the denominator of Eq. \ref{eq:lnLambda}.  Second, $\ln\Lambda = \ln(E_{\rm C}/E_{\rm crit})$, where $E_{\rm C}$ is the cascade energy, and $E_{\rm crit}\approx 10^8$ eV is known as the critical energy \cite{PhysRevD.105.123019}.  Since $\ln\Lambda = \ln E_{\rm C} - \ln E_{\rm crit}$, separating this ratio adds $\log_{10} E_{\rm crit}$ to the right hand side of Eq. \ref{eq:lnLambda}.  Third, let $c_{\rm ave}$ be the average of $c_{\rm em}$ and $c_{\rm had}$, accurate to 0.05 m.  The average reflects the unknown hadronic or electromagnetic nature of the cascade.  The modified form of Eq. \ref{eq:lnLambda} is

\begin{equation}
\log_{10} E_{\rm C} = \frac{\left( c\sigma_t \right)^2}{\ln 10(c_{\rm ave} \Delta\theta_{\rm rms}\sin\theta_{\rm C})^2} + \log_{10} E_{\rm crit} \label{eq:lnLambda_2}
\end{equation}

@@

Multiple signals occur within traces either when signals from two ray-tracing paths are available, or when part of the signal reflects from the surface back to the channel.  Signals that propagate directly to the detector are known as \textit{direct signals}, while signals that reflect at the snow-air interface are known as \textit{reflected signals}.  Complex RF signal propagation in polar ice has been studied, and even proposed as a UHE-$\nu$ energy reconstruction technique \cite{Barwick:2018497,anker2019neutrino-734,deaconu2018measurements-182}.  When two signals are present in the voltage trace, the fitting algorithm favors $\sigma_t$ values that are unphysically larger than the average quoted in Tab. \ref{tab:2}.  This systematically overestimates $\log_{10} E_{\rm C}$.  Though it is straightforward to add a second analytic envelope to the fit algorithm to account for multiple pulses, this was beyond the scope of this work.  An example of a CSW event with direct and reflected components fit by an analytic envelope is shown in Fig. \ref{fig:example_waveforms_2}.

@@

In Secs. \ref{sec:int} and \ref{sec:unit}, previous work in the utility of analytic Askaryan models was reviewed, and important parameters were defined.  In Sec. \ref{sec:onc}, a fully analytic model for $\mathcal{E}_{\rm s*r}(t)$ and $s(t) * r(t)$ was presented and checked for accuracy.  In Sec. \ref{sec:sim}, the analytic model was shown to reject all but 0.2 RF thermal triggers in a 5 year run at a 1 Hz thermal trigger rate using a correlation threshold of $\rho\geq 0.4$.  The threshold $\rho\geq 0.4$ preserves 99.99\% of UHE-$\nu$ signals at 100 PeV.  The correlation distribution for UHE-$\nu$ signals peaked at 0.94, and some values even exceed 0.94.  Finally, in Sec. \ref{sec:recon}, a first attempt to reconstruct $\log_{10}E_{\rm C}$ using the CSW fit with data from a \textit{a single-string detector} was presented.  Though the error range for $\log_{10}E_{\rm C}$ was large, the average value was correct: $\log_{10}E_{\rm C} = 16.5 \pm 2.0$ for 100 PeV.

There are three logical steps for this work in the future.  First, we must account for multiple pulses in the algorithm used to fit the analytic envelope to CSWs from NuRadioMC.  The authors of \cite{anker2019neutrino-734} have shown how direct and reflected (DnR) signals may be used to constrain the UHE-$\nu$ energy.  This procedure should be combined with the analytic envelope fit to advance UHE-$\nu$ energy reconstruction.  Though this is not difficult to implement in NuRadioMC, it was beyond the scope of this work.

@@

Third, it is interesting to note that the model in this work relies on the \textit{off-cone} ($\theta \neq \theta_{\rm C}$) version of $s(t)$.  HH2022 also includes an \textit{on-cone} version of $s(t)$ that is used when $\Delta\theta = 0$, and can be used as $\Delta\theta\to 0$.  The on-cone model could provide a better fit between $\mathcal{E}_{\rm s*r}(t)$ for events with $\Delta\theta \lesssim 1$ degree.  Further, the on-cone model is defined in a piecewise fashion by rising and falling exponential functions, making the convolution with Eq. \ref{eq:r} easier than the procedure used to arrive at Eqs. \ref{eq:final}-\ref{eq:final2}.

We would like to thank Prof. Steve Barwick, and Prof. Mark Kozek for useful background discussions.  We are grateful to the authors of RB, Prof. John Ralston and Roman Buniy, for inspiring us in this line of research \cite{10.1103/physrevd.65.016003}.  We would like to thank Prof. Dave Besson for encouragement and wisdom while we continued to develop the model.  Most of all, we would like to thank Prof. Amy Connolly for inspiring us and encouraging us to master more advanced applications of complex analysis to mathematical physics.  We hope the model will help identify the first UHE-$\nu$ via the Askaryan effect, especially in light of potential UHE-$\nu$ observations \cite{collaboration2025observation-22f}.

@@

\small
\begin{verbatim}
import numpy as np
from scipy.integrate import quad
from scipy.special import dawsn as D
...
def shifted_laplace_transform(...):
...
def math_env(self,t,E0,R0,sigma_t,f0,gamma):
    units = R0*E0*sigma_t*sigma_t
    J = complex(0,1)
    x = t/(sigma_t*np.sqrt(2))
    z = (2*np.pi*J*f0-2*np.pi*gamma)
    z *= np.sqrt(2)*sigma_t
    k=-z
    q = -J*(x+z/2)
    first = -np.sqrt(np.pi)*(x*np.exp(-x*x)*w(q)
        +0.5*J*np.exp(-x*x)*self.dwdq(q))
    second = 2/np.sqrt(np.pi)*(D(x)
        +k*self.shifted_laplace_transform(D,k,x))
    if(np.isinf(first) or np.isinf(second) 
        or np.isnan(first) or np.isnan(second)):
        return 0.0
    else:
        result = units*(first+J*second)
    return 0.5*np.abs(result)
\end{verbatim}

>>>>

\title{Complex Analysis of Askaryan Radiation: UHE-$\nu$ Identification and Reconstruction using the Hilbert Envelope of Observed Signals}

@@

Cosmic neutrinos with energies up to 100 PeV have been detected by the IceCube and KM3NeT collaborations \cite{10.1126/science.1242856,aartsen2013first-bff,collaboration2016observation-03b,collaboration2018neutrino-2a0,collaboration2021detection-6fa,collaboration2022evidence-a08,collaboration2023observation-08b,collaboration2025observation-22f}. Previous analyses indicate that the discovery of UHE-$\nu$ flux above 5 PeV requires large Askaryan-class detectors \cite{10.1103/physrevd.98.062003}.  UHE-$\nu$ could reveal the source of ultra-high energy cosmic rays (see sections 3.1-3.3 of \cite{10.48550/arxiv.2008.04323}).  Further, studying electroweak interactions at these energies is impossible on Earth, and Askaryan-class neutrino detectors will provide new data (see section 3.4 of \cite{10.48550/arxiv.2008.04323}).

@@

Askaryan-class detectors actually observe voltage traces that represent the RF detection channel response, convolved with $\vec{E}$-fields that have propagated through kilometers of polar ice.  NuRadioMC accounts for these effects by incorporating measurements from years of lab and field work \cite{10.1016/j.astropartphys.2014.09.002,10.3189/2015jog14j214,10.3189/2015jog15j057,saltzberg,10.1103/PhysRevD.74.043002,ask_ice,10.1140/epjc/s10052-020-7612-8,Barwick:2018497,ALLISON201963,10.1088/1748-0221/15/09/p09039,deaconu2018measurements-182,welling2024brief-b47}.  In this work, we present the first fully analytic Askaryan model in the time-domain that matches the observed voltage traces.  In practice, it is common to compute the Hilbert envelope of voltage traces from RF channels before cross-correlating them.  This is done to remove oscillations introduced by the RF antennas in the channels, which can confuse cross-channel timing and reconstruction.  Our calculations include both the voltage trace, and the Hilbert envelope of the trace.  The work is organized as follows.  Units, definitions, and notational conventions are given in Sec. \ref{sec:unit}.  The calculations of the observed voltage trace and Hilbert envelope of the trace are given in Sec. \ref{sec:onc}.  These results are compared to NuRadioMC output in Sec. \ref{sec:sim}.  In Sec. \ref{sec:recon}, a preliminary reconstruction of the logarithm of the cascade energy from the UHE-$\nu$ interaction is given.  The key findings are summarized in Sec. \ref{sec:conc}.

@@

The analysis is based on two analytic functions: the Askaryan signal, $s(t)$, and the RF channel response, $r(t)$.  The RF detection channel is a linear, time-invariant DSP system.  Thus, the observed voltage trace in an Askaryan-class detector is the convolution of $r(t)$ and $s(t)$, $r(t) * s(t)$.  Let $\hat{s}(t)$ represent the Hilbert transform of $s(t)$, and let $j=\sqrt{-1}$.  The \textit{analytic signal}, $s_a(t)$, and \textit{signal envelope}, $\mathcal{E}_s(t)$, are defined by

@@

The $n_{\rm max}$ parameter is the maximum number of excess negative cascade charges, and the overall RF amplitude, $E_{\rm 0}$, is propotional to $n_{\rm max} a$ \cite{10.1103/physrevd.65.016003}.  JCH+AC and HH2022 demonstrated that the frequency $\omega_{\rm 0}$ is related to the ICD and the cascade form factor \cite{10.1016/j.astropartphys.2017.03.008,PhysRevD.105.123019}.  Monte Carlo simulations have shown that the lateral dependence of the ICD is exponentially distributed \cite{zhs,10.1016/j.astropartphys.2017.03.008}.  JCH+AC derived the form factor by modeling the lateral component of the ICD as an exponential distribution, which in turn makes the form factor act as a low-pass filter with cutoff $\omega_0$.  Finally, the authors of HH2022 showed that $p$ in Tab. \ref{tab:param} is related to $\sigma_t$, the pulse width of $s(t)$ \cite{PhysRevD.105.123019}:

@@

The parameters in Eq. \ref{eq:s_full} that do not depend on time can be folded into a single constant, $E_0$, leaving only the time-dependence.  From now on, let $t$ refer to $t_{\rm r}$, without the subscript.  The signal model $s(t)$ is
\begin{equation}
s(t) = -E_0 t e^{-\frac{1}{2}\left(t/\sigma_t\right)^2} \label{eq:s}
\end{equation}
This is the \textit{off-cone} equation from \cite{PhysRevD.105.123019}.  The parameter $\sigma_{\rm t}$ is the pulse width, and it depends two quantities: $a$ and $\Delta\theta$ (Eq. \ref{eq:uncert}).  The parameter $E_0$ is the amplitude normalization, and the dependencies on other parameters can be determined from Eq. \ref{eq:s_full} and Tab. \ref{tab:param}.  The most important of these is the $1/r$ dependence (Eq. \ref{eq:s_full}).  To achieve the goal of $\mathcal{E}_{\rm r * s}(t)$, the Hilbert transform and analytic signal of $s(t)$ are required.  The Hilbert transform $\widehat{s}(t)$ is equivalent to the convolution of $s(t)$ and the tempered distribution $h(t) = 1/(\pi t)$.  The implication in the Fourier domain is that the negative frequencies in the spectrum of $\hat{s}(t)$ vanish, while the positive ones are doubled.  Let the $\sgn(f)$ be $-1$ if $f<0$, $0$ if $f=0$, and $1$ if $f>1$, and let $S(f)$ be the Fourier transform of $s(t)$.  The Fourier transform of the analytic signal $s_a(t)$ is
\begin{equation}
\mathcal{F}\lbrace s_{\rm a}(t) \rbrace_{f} = S_{\rm a}(f) = S(f)(1+\sgn{f}) \label{eq:sa_1}
\end{equation}
Thus, if $f<0$, $S_a(f) = 0$, and $S_a(f) = 2S(f)$ if $f\geq 0$.  Taking the inverse Fourier transform of Eq. \ref{eq:sa_1}, the analytic signal may be written in terms of $S(f)$:
\begin{equation}
s_{\rm a}(t) = 2\int_{0}^{\infty} S(f) e^{2\pi j f t} df \label{eq:sa_2}
\end{equation}
 The Fourier transform of Eq. \ref{eq:s} is
\begin{equation}
S(f) = E_0 \sigma_t^3 (2\pi)^{3/2} j f e^{-2\pi^2 f^2 \sigma_t^2}
\end{equation}
Using the gaussian spectral width $\sigma_{\rm f}$ from \cite{10.1016/j.astropartphys.2017.03.008}, and the guassian width of $s(t)$ from \cite{PhysRevD.105.123019}, it was shown in \cite{PhysRevD.105.123019} that the uncertainty principle holds for off-cone signals:
\begin{equation}
\sigma_t \sigma_f \geq \frac{1}{2\pi}
\end{equation}
The equality is reached in the limit the far-field parameter limits to zero: $\eta \to 0$.  This makes the signal spectrum
\begin{equation}
S(f) = E_0 \sigma_t^3 (2\pi)^{3/2} j f e^{-\frac{1}{2}\left(f/\sigma_f\right)^2} \label{eq:spec}
\end{equation}
Inserting $S(f)$ into Eq. \ref{eq:sa_2}, $s_{\rm a}(t)$ is
\begin{equation}
s_{\rm a}(t) = \frac{E_0 \sigma_t^3 (2\pi)^{3/2}}{\pi} \frac{d}{dt}\int_0^{\infty} e^{-\frac{1}{2}\left(f/\sigma_f\right)^2} e^{2\pi j f t} df \label{eq:sa_3}
\end{equation}
 Let $k^2/4 = \frac{1}{2}\left(f/\sigma_f\right)^2$, and $x = t/(\sqrt{2}\sigma_t)$.  Equation \ref{eq:sa_3} can be broken into real and imaginary parts:
\begin{align}
s_{\rm a}(t) &= \frac{E_0 \sigma_{\rm t}}{\sqrt{2\pi}}\frac{dI}{dx} \\
\Re\lbrace I \rbrace &= \int_0^{\infty} e^{-k^2/4}\cos(kx) dk \\
\Im\lbrace I \rbrace &= \int_0^{\infty} e^{-k^2/4}\sin(kx) dk
\end{align}
The real part of $I$ is even, so it can be extended to $(-\infty,\infty)$ if it is multiplied by $1/2$.  The result is
\begin{equation}
\Re\lbrace I \rbrace = \sqrt{\pi} e^{-x^2}
\end{equation}
The imaginary part of $I$ is proportional to the \textit{Dawson function, $D(x)$} \cite{NIST:DLMF}:
\begin{equation}
\Im\lbrace I\rbrace = 2 D(x)
\end{equation}
 The overall analytic signal, $s_a(t)$, is
\begin{equation}
s_a(t) = -E_0 \left(t e^{-\frac{1}{2}\left(t/\sigma_t\right)^2} - \frac{2 j\sigma_t}{\sqrt{2\pi}} \frac{dD(x)}{dx}\right) \label{eq:sa_4}
\end{equation}
The envelope of the signal, $\mathcal{E}_s(t)$, is the magnitude of Eq. \ref{eq:sa_4}.  Though $D(x)$ is not evaluated analytically, a high-precision algorithm for computing $D(x)$ was given in \cite{10.1063/1.4822832}.  As expected, $|s_a(0)| \neq 0$, since $dD(x)/dx = 1 - 2x D(x)$.

@@

To reduce uncertainties, the Hilbert envelope of observed data is used in cross-correlations instead of the original signals.  Thus, an analytic prediction for the Hilbert envelope of the observed data would an effective signal template.  An assumption must be made, however, for the RF channel response, $r(t)$.  The RLC impulse response was first used by RICE at the South Pole at a model for RF dipole channels \cite{10.1103/PhysRevD.85.062004}.  The RLC damped oscillator is a suitable circuit model for the RF dipole channels for two reasons.  First, dipoles respond within a bandwidth centered around a resonance frequency, just as RLC circuits do.  Second, RF dipole channels are used in RICE, ARA, RNO-G, and the proposed IceCube Gen2 because these channels must fit inside cylindrical ice boreholes \cite{10.1103/PhysRevD.85.062004,10.1103/physrevd.102.043021,10.1016/j.astropartphys.2011.11.010,10.1088/1748-0221/16/03/p03025,10.48550/arxiv.2008.04323}.  Thus, the model chosen for $r(t)$ is the damped oscillation of an RLC circuit.

@@

NuRadioMC was used to generate UHE-$\nu$ interactions in a cylindrical ice volume (see Tab. \ref{tab:1}).  The 100 PeV interactions included charged and neutral electroweak currents, and the LPM effect.  The Askaryan model used in NuRadioMC was AHRZ2020 \cite{PhysRevD.101.083005}.  AHRZ2020 is a \textit{semi-analytic} parameterization of the Askaryan effect, in which a vector potential $\vec{A}(\vec{r},t)$ is convolved with the profile of the net charge in the UHE-$\nu$ cascade.  AHRZ2020 accounts for sub-cascades and the LPM effect, and it has been validated against MC simulations \cite{zhs,10.1103/physrevd.84.103003}.  The Askaryan model used in NuRadioMC for this analysis was \textit{not} HH2022, so correlations between MC output and Eqs. \ref{eq:final}-\ref{eq:final2} are solely on physical grounds.

@@

\begin{equation}
\ln\Lambda = \left( \frac{c\sigma_t}{x_{\rm em/had} \Delta\theta_{\rm rms}\sin\theta_{\rm C}} \right)^2 \label{eq:lnLambda}
\end{equation}

Using Eqs. 10 and 12 from HH2022 (\cite{PhysRevD.105.123019}), $x_{\rm em}$ and $x_{\rm had}$ were found to be 0.80 and 0.93 meters, respectively (FWHM, $R=0.5$).  Using Eq. \ref{eq:lnLambda}, the $\sigma_t$ results from the optimized envelope fits to UHE-$\nu$ signals may be used to deduce the logarithm of the UHE-$\nu$ cascade, $\log_{10} E_{\rm C}$.  First, converting to the base-10 logarithm introduces a factor of $\ln(10)$ in the denominator of Eq. \ref{eq:lnLambda}.  Second, $\ln\Lambda = \ln(E_{\rm C}/E_{\rm crit})$, where $E_{\rm C}$ is the cascade energy, and $E_{\rm crit}\approx 10^8$ eV is known as the critical energy \cite{PhysRevD.105.123019}.  Since $\ln\Lambda = \ln E_{\rm C} - \ln E_{\rm crit}$, separating this ratio adds $\log_{10} E_{\rm crit}$ to the right hand side of Eq. \ref{eq:lnLambda}.  Third, let $x_{\rm ave}$ be the average of $x_{\rm em}$ and $x_{\rm had}$, accurate to 0.05 m.  The average reflects the unknown hadronic or electromagnetic nature of the cascade.  The modified form of Eq. \ref{eq:lnLambda} is

\begin{equation}
\log_{10} E_{\rm C} = \frac{\left( c\sigma_t \right)^2}{\ln 10(x_{\rm ave} \Delta\theta_{\rm rms}\sin\theta_{\rm C})^2} + \log_{10} E_{\rm crit} \label{eq:lnLambda_2}
\end{equation}

@@

Multiple signals occur within traces either when signals from two ray-tracing paths are available, or when part of the signal reflects from the surface back to the channel.  Signals that propagate directly to the detector are known as \textit{direct signals}, while signals that reflect at the snow-air interface are known as \textit{reflected signals}.  Complex RF signal propagation in polar ice has been studied, and even proposed as a UHE-$\nu$ energy reconstruction technique \cite{Barwick:2018497,anker2019neutrino-734,deaconu2018measurements-182}.  When two signals are present in the voltage trace, the fitting algorithm favors $\sigma_t$ values that are unphysically larger than the average quoted in Tab. \ref{tab:2}.  This systematically overestimates $\log_{10} E_{\rm C}$.  Though adding a second analytic envelope to the fit algorithm to account for pulse reflection is straightforward, this added complexity was beyond the scope of this work.  An example CSW event with direct and reflected signals fit by an analytic envelope is shown in Fig. \ref{fig:example_waveforms_2}.

@@

In Secs. \ref{sec:int} and \ref{sec:unit}, previous work in the utility of analytic Askaryan models was reviewed, and important parameters were defined.  In Sec. \ref{sec:onc}, a fully analytic model for $\mathcal{E}_{\rm s*r}(t)$ and $s(t) * r(t)$ was presented and checked for accuracy.  In Sec. \ref{sec:sim}, the analytic model was shown to reject all but 0.2 RF thermal triggers in a 5 year run at a 1 Hz thermal trigger rate using a correlation threshold of $\rho\geq 0.4$.  The threshold $\rho\geq 0.4$ preserves 99.99\% of UHE-$\nu$ signals at 100 PeV.  The correlation distribution for UHE-$\nu$ signals peaked at 0.94, and some values even exceed 0.94.  Finally, in Sec. \ref{sec:recon}, a first attempt to reconstruct $\log_{10}E_{\rm C}$ using the CSW fit with data from a \textit{a single-string detector} was presented.  Though the error range for $\log_{10}E_{\rm C}$ was large, the average value was correct: $\log_{10}E_{\rm C} = 16.7 \pm 2.0$ for 100 PeV.

There are three logical steps for this work in the future.  First, we must account for multiple pulses in the algorithm used to fit the analytic envelope to CSWs from NuRadioMC.  The authors of \cite{anker2019neutrino-734} have shown how direct and reflected (DnR) signals may be used to constrain the UHE-$\nu$ energy.  This procedure should be combined with the analytic envelope fit to advance UHE-$\nu$ energy reconstruction.  Though this is not difficult to implement, it was beyond the scope of this work.

@@

Third, it is interesting to note that the model in this work relies on the \textit{off-cone} ($\theta \neq \theta_{\rm C}$) version of $s(t)$.  HH2022 also includes an \textit{on-cone} version of $s(t)$ that is used when $\Delta\theta = 0$, and can be used as $\Delta\theta\to 0$.  The on-cone model could provide a better fit between $\mathcal{E}_{\rm s*r}(t)$ for events with $\Delta\theta \lesssim 1$ degree \cite{PhysRevD.105.123019}.  Further, the on-cone model is defined in a piecewise fashion by rising and falling exponential functions, making the convolution with Eq. \ref{eq:r} easier than the procedure used to arrive at Eqs. \ref{eq:final}-\ref{eq:final2}.

We would like to thank Prof. Steve Barwick, and Prof. Mark Kozek for useful background discussions.  We are grateful to the authors of RB, Profs. John Ralston and Roman Buniy, for inspiring us in this line of research \cite{10.1103/physrevd.65.016003}.  We would like to thank Prof. Dave Besson for encouragement and wisdom while we continued to develop the model.  Most of all, we would like to thank Prof. Amy Connolly for inspiring us and encouraging us to master more advanced applications of complex analysis to mathematical physics.  We hope the model will help identify the first UHE-$\nu$ via the Askaryan effect, especially in light of potential UHE-$\nu$ observations \cite{collaboration2025observation-22f}.

@@

\small
\begin{verbatim}
import numpy as np
from scipy.integrate import quad
from scipy.special import wofz as w
from scipy.special import dawsn as D
...
def shifted_laplace_transform(...):
...
def dwdq(q):
    J = complex(0,1)
    return 2*J/np.sqrt(np.pi)-2*q*w(q)
def math_env(self,t,E0,R0,sigma_t,f0,gamma):
    units = R0*E0*sigma_t*sigma_t
    J = complex(0,1)
    x = t/(sigma_t*np.sqrt(2))
    z = (2*np.pi*J*f0-2*np.pi*gamma)
    z *= np.sqrt(2)*sigma_t
    k=-z
    q = -J*(x+z/2)
    first = -np.sqrt(np.pi)*(x*np.exp(-x*x)*w(q)
        +0.5*J*np.exp(-x*x)*self.dwdq(q))
    second = 2/np.sqrt(np.pi)*(D(x)
        +k*self.shifted_laplace_transform(D,k,x))
    if(np.isinf(first) or np.isinf(second) 
        or np.isnan(first) or np.isnan(second)):
        return 0.0
    else:
        result = units*(first+J*second)
    return 0.5*np.abs(result)
\end{verbatim}
